## `r trait_list[[i]]$name`: Data summary and exploratory analysis

\

### Assessment of `r options`

\

Favorability scores are shown for the trait '`r tolower(trait_list[[i]]$name)`' which was collected during the data collection moment '`r trait_list[[i]]$assessment`'. The `r rankers` were asked to evaluate the best and worst `r option` based on your pre-defined questions: '`r trait_list[[i]]$question`'. The table below shows the number of times each `r option` was tested and the proportion of times it was ranked as the best or worst. Net favorability score is the difference between the best and worst ranks for each `r option``.

\

```{r}
f2 <- fav_traits[[1]][[i]]

knitr::kable(f2[nrow(f2):1, ],
             row.names = FALSE,
             caption = paste0("Table 3.", i, ".1. Favorability scores for '",
                              ClimMobTools:::.title_case(trait_list[[i]]$name),"'"))
```

\

Figure 3.`r i`.1. is a graphical representation of the content presented in Table 3.`r i`.1 showing the net favorability scores for the trait '`r ClimMobTools:::.title_case(trait_list[[i]]$name)`'.

```{r, include=FALSE, echo=FALSE}
f1 <- fav_traits[[2]][[i]]

```


```{r, dpi=dpi, fig.height=favplot_h, fig.width=6, fig.cap= paste0("Figure 3.", i, ".1. Net favorability scores for '", ClimMobTools:::.title_case(trait_list[[i]]$name),"'.")}
f1
```

\


### Plackett-Luce Model estimates

\
Table 3.`r i`.2 shows the results from the likelihood ratio test from the Plackett-Luce model for '`r ClimMobTools:::.title_case(trait_list[[i]]$name)`'. The hypothesis being tested is that there is no difference in the assessments of any of the different `r options`.

\

```{r}
aov_ii <- aov_tables[[i]]
if (length(aov_ii) > 1) {
  kable(aov_ii,
        row.names = FALSE,
        caption = paste0("Table 3.", i,".2. Likelihood ratio test results from fitted Plackett-Luce model with rankings for '", ClimMobTools:::.title_case(trait_list[[i]]$name), "'."))
}

```

\

Figure 3.`r i`.2 shows the estimates of the model coefficients with `r paste0(ci_level * 100, "%")` confidence intervals.  

\

```{r dpi=dpi, fig.height=favplot_h, fig.width=5, fig.cap=paste0("Figure 3.", i,".2. Plackett-Luce Model estimates (log-worth) of tested ", options, " for '", ClimMobTools:::.title_case(trait_list[[i]]$name),"' with ", ci_level*100, "% confidence intervals. Different letters indicate significant differences at p < ", sig_level ,". The ", option, " ", reference, " is set as reference (log-worth arbitrarily set to zero).")}

if(length(aov_ii) > 1){
plot_summaries[[i]] +
    labs(y = Option)
}
```

\

The probability of each `r option` being considered to be the top ranked `r option` (worth parameter) in a direct comparison between all the possible `r options` for '`r ClimMobTools:::.title_case(trait_list[[i]]$name)`' is presented in Figure 3.`r i`.3.

\

```{r, dpi=dpi, fig.height=favplot_h, fig.width=5, fig.cap=paste0("Figure 3.", i,".3. Worth parameters of tested ", options, " for the trait '", ClimMobTools:::.title_case(trait_list[[i]]$name), "'.")}
worth_plot[[i]]
```

\pagebreak
