## `r trait_list[[i]]$name`: Data summary and exploratory analysis

\

### Assessment of `r options`

\

Favorability scores are shown for the trait '`r tolower(trait_list[[i]]$name)`' which was collected during the data collection moment registered as '`r trait_list[[i]]$assessment`'. The `r rankers` were asked to evaluated the best and worst `r option` based on the question: '`r trait_list[[i]]$question`'.

\

```{r}
f2 <- fav_traits[[i]][[2]]

knitr::kable(f2[nrow(f2):1, ],
             row.names = FALSE,
             caption = paste0("Table 3.", i, ".1. Favorability scores for '",
                              tolower(trait_list[[i]]$name),"'"))
```

\

Figure 3.`r i`.1. is a graphical representation of the content presented in Table 3.`r i`.1 showing the net favorability scores for the trait '`r tolower(trait_list[[i]]$name)`'.

```{r, include=FALSE, echo=FALSE}
f1 <- fav_traits[[i]][[1]]
p2 <- 
  plot(f1) +
  xlab("") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, color = "#000000"),
        axis.text.y = element_text(size = 10, color = "#000000"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none")

```


```{r, dpi=dpi, fig.height=favplot_h, fig.width=6, fig.cap= paste0("Figure 3.", i, ".1. Net favorability scores for '",tolower(trait_list[[i]]$name),"'.")}
p2
```

\

### Pairwise contests

```{r}
vic_i <- vic_traits[[i]]
```

\

Figure 3.`r i`.2 shows the outcomes of all pairwise contests between the `r options` included in the project for '`r tolower(trait_list[[i]]$name)`'. Each panel shows the performance of one `r option` against all the other `r options` and shows the percentage of the times in which the panelled `r option` was ranked above the other `r options` shown as bars.


\

```{r,dpi=dpi, fig.height=contest_h, fig.width=9, fig.cap=paste0("Figure 3.", i, ".2. Head-to-head performance for '",tolower(trait_list[[i]]$name),"'.")}
plot(vic_i) + 
  labs(y = "", x = "") + 
  theme_minimal() +  
  theme(axis.text.x = element_text(size = 10, color = "#000000"),
        axis.text.y = element_text(size = 10, color = "#000000"),
        strip.text.x = element_text(size = 11, color = "#000000", face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none")

```

\

### Plackett-Luce Model estimates

\
Table 3.`r i`.2 shows the results from the likelihood ratio test from the Plackett-Luce model for '`r tolower(trait_list[[i]]$name)`'. The hypothesis being tested is that there is no difference in the assessments of any of the different `r options`.

\

```{r}
aov_ii <- aov_tables[[i]]
if (length(aov_ii) > 1) {
  kable(aov_ii,
        row.names = FALSE,
        caption = paste0("Table 3.", i,".2. Likelihood ratio test results from fitted Plackett-Luce model with rankings for '", tolower(trait_list[[i]]$name), "'."))
}

```

\

Figure 3.`r i`.3 shows the estimates of the model coefficients with `r paste0(ci_level * 100, "%")` confidence intervals.  

\

```{r dpi=dpi, fig.height=favplot_h, fig.width=5, fig.cap=paste0("Figure 3.", i,".3. Plackett-Luce Model estimates (log-worth) of tested ", options, " for '", tolower(trait_list[[i]]$name),"' with ", ci_level*100, "% confidence intervals. Different letters indicate significant differences at p < ", sig_level ,". The ", option, " ", reference, " is set as reference (log-worth arbitrarily set to zero).")}

if(length(aov_ii) > 1){
plot_summaries[[i]] +
    labs(y = Option)
}
```

\

The same information from Figure 3.`r i`.3 is shown in Table 3.`r i`.3.

\

```{r}
if (length(aov_ii) > 1) {
  ms_i <- summaries[[i]]
  kable(ms_i, 
        digits = 4,
        row.names = FALSE,
        caption = paste0("Table 3.", i,".3. Model coefficients and mean separation of Plackett-Luce model for '",
                         tolower(trait_list[[i]]$name),"' with ", ci_level*100, "% confidence intervals."))
}
```

\

Table 3.`r i`.4 and Figure 3.`r i`.4 use the coefficients from the Plackett-Luce model of rankings from the evaluation on '`r tolower(trait_list[[i]]$name)`' to estimate the probability of each `r option` being considered to be the top ranked `r option` in a direct comparison between all of the possible `r options`.

\


```{r}
if (length(aov_ii) > 1) {
  
  kable(worths[[i]][,-2],
      row.names = FALSE,
      caption = paste0("Table 3.", i,".4. Percentage probability of being highest ranked for '",
                      tolower(trait_list[[i]]$name), "'."))
  
}
```

\

```{r, dpi=dpi, fig.height=favplot_h, fig.width=5, fig.cap=paste0("Figure 3.", i,".4. Probability of being the best ranked for '", tolower(trait_list[[i]]$name),"'.")}
x <- worths[[i]]
plot_worth_bar(x, value = "Worth", group = Option)
```

\pagebreak
