---
title: "`r paste('Analysis Report of ClimMob project ', projname)`"
author: "Automated Report by ClimMob"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    reference_docx: word_style_template.docx
  html_document:
    toc: true
  pdf_document:
    toc: true
bibliography: ["climmob.bib"]
---

```{r setup_opts, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,error = FALSE,message=FALSE,warning = FALSE)
```

You are reading a report generated by ClimMob. This is a software package to analyze data generated by citizen science or crowdsourcing.

# Introduction  

In agriculture, the local environmental conditions determine to a large degree which technological solutions are the most suitable. In dry soils, for example, drought-resistant crop varieties will outperform other varieties, but in wet soils these same varieties may do worse than most. Not only drought, but an entire range of problems including excessive heat, floods, new pests and diseases tend to intensify under climate change. This multitude of limiting factors requires multiple technological solutions, tested in diverse environments. 
 
Citizen science is based on the cooperation of citizen scientist or observers (paid or unpaid). Researchers assign microtasks (observations, experiments) that, once completed and gathered, contribute with a great amount of information to science. One of the advantages of citizen science is that agricultural researchers can get access to many environments by crowdsourcing their experiments. As farmers contribute with their time, skills and knowledge to the investigation, researchers are able to do more tests than in a traditional setup. Also citizen scientists acquire new knowledge, abilities and information useful for future challenges of their work.

## ClimMob

The primary goal of ClimMob is to help farmers adapt to variable and changing climates. ClimMob was created as part of Bioversity International's research in the CGIAR Research Programme on Climate Change, Agriculture, and Food Security (CCAFS). It serves to prepare and analyze citizen science experiments in which a large number of farmers observe and compare different technological options under a wide range environmental conditions [@vanEtten2019tricot]. 
 
ClimMob software assigns a limited number of items (typically 3 crop varieties or agricultural practices) to each farmer, who will compare their performance. Each farmer gets a different combination of items drawn from a much larger set of items. Comparisons of this kind are thought to be a very reliable way to obtain data from human observers. Once the results of the microtasks have been collected, ClimMob builds an image of the whole set of assigned objects, combining all observations. ClimMob not only reconstructs the overall ordering of items, but also takes into account differences and similarities between observers and the conditions under which they observe. It assigns similar observers to groups that each corresponds to a different preference profile. Groups are created on the basis of whichever variables which have been collected, that are found to be significantly linked to the preferences.
 
ClimMob uses Plackett-Luce models to analyze ranking data [@Turner2020]. It automatically generates analytical reports, as well as individualized information sheets for each participant. 
 

## How to cite

If you publish any results generated with ClimMob, you should cite a number of articles as the package builds on various contributions. Van Etten [-@vanEtten2019tricot] introduced the crowdsourcing philosophy behind ClimMob. It is important to mention that ClimMob is implemented in `R`, a free, open-source analysis software [@RCoreTeam]. Methodologically, if you report on the tree results, you should mentioned that ClimMob applies the Plackett-Luce model published by Turner et al. [-@Turner2020]. To cite ClimMob itself, mention van Etten et al. [-@climmob].

# Section 1: Headline Results

Overall there were `r nranker` `r rankers` participating in this study. Each `r ranker` assessed `r ncomp` different `r options` and ranked them in order of their overall preference. In addition they also provided rankings for `r ntrait` additional traits: 

```{r traits}

kable(data.frame("Short name" = pars$chars$char,
                 "Question"   = pars$chars$char_full,
                 check.names = FALSE), 
      align = "l")

```


Table 1 provides a list of the `r options` assessed within this trial, with the frequency and percentage of `r rankers` who assessed each `r option`.

```{r itemtable}
kable(itemtable, 
      caption = paste0("Table 1: Frequency of ", options," assessed"),
      align = "l")
```

# References